Bioinformatics Assignment 3

### 2016-02-29 bioinformatics/latex/a3.tex
bla

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.45\textwidth]{h3-clustalw.png}
  \includegraphics[width=0.45\textwidth]{h3-phyml.png}
  \caption{ClustalW tree on left for H3, Phyml tree on right. 332-Arabidopsis, 156-human, 688-zebrafish,
  387-mouse, 787-drosophila melanogaster, 327-tobacco.}
\end{figure}

@@

These two found motifs look almost identical. This suggests that there is only one
main motif in the sequences, so that one-occurence-per-sequence and any-number-of-occurrences
both finds the same number: one.\\

@@

\textbf{a.)}
chr1 72 145 region1 100 + $\rightarrow$ chr1 progname feature 73 145 100 +\\
chr1 221 342 region2 100 + $\rightarrow$ chr1 progname feature 222 221 100 +\\
chr1 473 577 region3 100 + $\rightarrow$ chr1 progname feature 474 473 100 +\\

Here progname is the name of the generating program, BED does not specify it.\\

\textbf{b.)}
chr1 myDB gene 743 1200 . + . ID=gene1 $\rightarrow$ chr1 742 1200 name . +
chr1 myDB gene 3405 5345 . + . ID=gene2 $\rightarrow$ chr1 3404 5345 name . +
chr3 myDB mRNA 9143 9778 . + . ID=transcript1 $\rightarrow$ chr1 9142 9778 name . +

@@

Pol II Chip Tissue 2:\\
We find the median of the gene body to be 1.3. We find the max $\pm$ 100 of the TSS
to be 1.3 as well.\\
\begin{align*}
  \frac{Max}{Median} &= \frac{1.3}{1.3} \approx 1
\end{align*}

We find the median to be 1.4 and the max to be 5.1.\\
Pol II Chip Tissue 1:\\
\begin{align*}
  \frac{Max}{Median} &= \frac{5.1}{1.4} \approx 3.64
\end{align*}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.45\textwidth]{h3-clustalw.png}
  \includegraphics[width=0.45\textwidth]{h3-phyml.png}
  \caption{ClustalW tree on left for H3, Phyml tree on right. 332-Arabidopsis,
    156-human, 688-zebrafish,387-mouse, 787-drosophila melanogaster, 327-tobacco.}
\end{figure}

@@

These two found motifs in Figure 2 look almost identical. This suggests that there is only one
main motif in the sequences, so that one-occurence-per-sequence and any-number-of-occurrences
both finds the same number: one. If there were more motifs that met the motifness-threshold,
they would be found by ANR but not OOPS. The fact that there is only one main motif is plausible:
there is one active site on the coded protein, the rest of the protein is free to mutate to meet
the species' needs.\\

@@

\textbf{a.)}\\
chr1 72 145 region1 100 + $\rightarrow$ chr1 progname feature 73 145 100 +\\
chr1 221 342 region2 100 + $\rightarrow$ chr1 progname feature 222 342 100 +\\
chr1 473 577 region3 100 + $\rightarrow$ chr1 progname feature 474 577 100 +\\

Here progname, feature are the names of the generating program and feature,
as BED does not specify them.\\

\textbf{b.)}\\
chr1 myDB gene 743 1200 . + . ID=gene1 $\rightarrow$ chr1 742 1200 name . +\\
chr1 myDB gene 3405 5345 . + . ID=gene2 $\rightarrow$ chr1 3404 5345 name . +\\
chr3 myDB mRNA 9143 9778 . + . ID=transcript1 $\rightarrow$ chr1 9142 9778 name . +\\

@@

\textbf{Pol II Chip Tissue 2:}\\
We find the median of the gene body {1.1, 1.1, 1.1, 1.5, 1.7} to be 1.1.
We find the max $\pm$ 100 of the TSS to be 1.3 by inspection.\\
\begin{align*}
  SI = \frac{Max}{Median} &= \frac{1.3}{1.1} \approx 1.18
\end{align*}

\textbf{Pol II Chip Tissue 1:}\\
We find the median of {1.3, 1.3, 1.3, 1.5, 1.5} to be 1.3 and the max within 100pm of
the TSS to be 5.1 by inspection.\\
\begin{align*}
  SI = \frac{Max}{Median} &= \frac{5.1}{1.3} \approx 3.92
\end{align*}
